### 2013-06-26 latex/SupportingText.tex
Updated SupportingText.tex by adding two more tables with max_theo_*, max_emp_* values and pop_* values. Checked main paper table Normalizing values, all clear.

\begin{center}
\footnotesize
\begin{tabular}{lccccc}
&  \multicolumn{2}{c}{Empirical} & ~~~& \multicolumn{2}{c}{Theoretical}\\\cline{2-3}\cline{5-6}
Residue & $\phi$ & $\psi$ & & $\phi$ & $\psi$ \\
\hline Alanine   & $-66.7^{\circ}$ & $-13.1^{\circ}$ & & $-60^{\circ}$ & $-15^{\circ}$\\
                 & $-52.1^{\circ}$ & $-33.6^{\circ}$ & &\\
                 & $-51.9^{\circ}$ & $-37.9^{\circ}$ & &\\
Arginine        & $-79.2^{\circ}$ & $-20.2^{\circ}$ & & $-70^{\circ}$ & $-5^{\circ}$ \\
		 &	&	& & $-70^{\circ}$ & $-25^{\circ}$\\
		 &	&	& & $-60^{\circ}$ & $-15^{\circ}$ to $-10^{\circ}$\\
		 &	&	& & $-55^{\circ}$ & $-30^{\circ}$\\
                 &      &       & & $-40^{\circ}$ & $-50^{\circ}$\\      
Asparagine       & $-94.8^{\circ}$ & $-3.4^{\circ}$ & & $-50^{\circ}$ & $-40^{\circ}$ \\
                 &      &       & & $-50^{\circ}$ & $-30^{\circ}$\\
		 &      &       & & $\phantom{-}70^{\circ}$ & ~\,$-5^{\circ}$\\
Aspartate    & $-79.4^{\circ}$ & $83.0^{\circ}$ & & $70^{\circ}$ & $-5^{\circ}$ \\
Cysteine        & $-87.7^{\circ}$ & $-45.1^{\circ}$ & & $60^{\circ}$ & $-40^{\circ}$ \\
Glutamine      & $-65.5^{\circ}$ & $-24.0^{\circ}$ & & $70^{\circ}$ & $-5^{\circ}$\\
Glutamate     & $-55.0^{\circ}$ & $-49.9^{\circ}$ & & $-60^{\circ}$ & $-15^{\circ}$\\
Glycine          & $80.2^{\circ}$ & $7.2^{\circ}$ & & $-75^{\circ}$ & $20^{\circ}$  \\
                 &      &       & & $-75^{\circ}$ & $50^{\circ}$\\
                 &      &       & & $-70^{\circ}$ & $0^{\circ}$\\
                 &      &       & & $-65^{\circ}$ & $-10^{\circ}$\\
                 &      &       & & $-60^{\circ}$ & $-15^{\circ}$\\
                 &      &       & & $-50^{\circ}$ & $-25^{\circ}$\\
                 &      &       & & $70^{\circ}$ & $-15^{\circ}$\\
                 &      &       & & $75^{\circ}$ & $-30^{\circ}$\\
Histidine        & $51.2^{\circ}$ & $32.4^{\circ}$ & & $-180^{\circ}$ & $155^{\circ}$  \\
		 &	 &	& & $-80^{\circ}$ & $170^{\circ}$ to $175^{\circ}$ \\
                 &       &      & & $-80^{\circ}$ to $-75^{\circ}$ & $130^{\circ}$ \\
Isoleucine      & $-64.1^{\circ}$ & $-21.9^{\circ}$ & & $-55^{\circ}$ & $-25^{\circ}$ \\
		&	&	& & $-50^{\circ}$ & $-40^{\circ}$ \\
Leucine         & $-81.6^{\circ}$ & $-13.5^{\circ}$ & & $-70^{\circ}$ & $-5^{\circ}$  \\
                & $-63.5^{\circ}$ & $-44.5^{\circ}$ & & & \\
                & $-60.9^{\circ}$ & $-29.3^{\circ}$ & & & \\
                & $-55.8^{\circ}$ & $-36.4^{\circ}$ & & & \\     
Lysine          & $63.1^{\circ}$ & $23.1^{\circ}$ & & $-45^{\circ}$ & $-45^{\circ}$ to $-40^{\circ}$ \\
Methionine      & $-67.5^{\circ}$ & $-27.5^{\circ}$ & & $50^{\circ}$ & $-40^{\circ}$  \\
Phenylalanine   & $-50.3^{\circ}$ & $135.2^{\circ}$ & & $-45^{\circ}$ & $-40^{\circ}$  \\
                &       &       & & $70^{\circ}$ & $-10^{\circ}$ \\
Proline         &  $-63.8^{\circ}$ & $-21.6^{\circ}$ & & $-55^{\circ}$ & $-20^{\circ}$  \\
Serine          & $-58.1^{\circ}$ & $-27.3^{\circ}$ & & $65^{\circ}$ & $-45^{\circ}$ \\
		& $-103.4^{\circ}$ & $1.1^{\circ}$ & & & \\
Threonine       & $-57.4^{\circ}$ & $-17.3^{\circ}$ & & $-45^{\circ}$ & $-45^{\circ}$  \\
Tryptophan      & $-68.0^{\circ}$ & $-62.3^{\circ}$ & & $65^{\circ}$ & $-40^{\circ}$ to $-35^{\circ}$  \\
		&       &       & & $70^{\circ}$ & $-55^{\circ}$  \\
Tyrosine        & $-67.6^{\circ}$ & $-9.8^{\circ}$ & & $-50^{\circ}$ & $-40^{\circ}$ to $-35^{\circ}$ \\
                &       &       & & $-45^{\circ}$ & $-45^{\circ}$ \\
Valine          & $-56.2^{\circ}$ & $-31.7^{\circ}$ & & $-55^{\circ}$ & $-25^{\circ}$  \\
\hline
\end{tabular}
\end{center}

>>>>

\begin{center}
\footnotesize
\begin{tabular}{lccccccccc}
Residue & max-emp-100 & max-emp-97 & max-emp-80 & max-emp-gen & & max-theo-100 & max-theo-97 & max-theo-80 & max-theo-gen\\
\hline Alanine   & $121$ & $121$ & $121$ & $121$ & & $138$ & $129$ & $128$ & $132$\\
Arginine         & $265$ & $265$ & $265$ & $265$ & & $285$ & $274$ & $274$ & $280$\\
Asparagine       & $187$ & $187$ & $187$ & $187$ & & $204$ & $195$ & $193$ & $199$\\
Aspartate        & $187$ & $187$ & $187$ & $187$ & & $204$ & $193$ & $192$ & $197$\\
Cysteine         & $148$ & $148$ & $133$ & $148$ & & $169$ & $167$ & $157$ & $167$\\
Glutamate        & $214$ & $214$ & $214$ & $214$ & & $233$ & $223$ & $222$ & $227$\\
Glutamine        & $214$ & $214$ & $214$ & $214$ & & $234$ & $225$ & $224$ & $228$\\
Glycine          & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & & $114$ & $104$ & $104$ & $109$\\
Histidine        & $216$ & $216$ & $216$ & $216$ & & $213$ & $209$ & $209$ & $209$\\
Isoleucine       & $195$ & $195$ & $195$ & $195$ & & $208$ & $197$ & $196$ & $201$\\
Leucine          & $191$ & $191$ & $191$ & $191$ & & $211$ & $201$ & $199$ & $205$\\
Lysine           & $230$ & $230$ & $229$ & $230$ & & $246$ & $236$ & $235$ & $240$\\
Methionine       & $203$ & $203$ & $203$ & $203$ & & $227$ & $224$ & $218$ & $226$\\
Phenylalanine    & $228$ & $228$ & $226$ & $228$ & & $251$ & $240$ & $236$ & $244$\\
Proline          & $154$ & $154$ & $154$ & $154$ & & $166$ & $159$ & $157$ & $164$\\
Serine           & $143$ & $143$ & $143$ & $143$ & & $161$ & $155$ & $150$ & $158$\\
Threonine        & $163$ & $163$ & $161$ & $163$ & & $182$ & $172$ & $171$ & $176$\\
Tryptophan       & $264$ & $264$ & $262$ & $264$ & & $295$ & $285$ & $282$ & $293$\\
Tyrosine         & $255$ & $255$ & $255$ & $255$ & & $274$ & $263$ & $262$ & $266$\\
Valine           & $166$ & $165$ & $165$ & $166$ & & $184$ & $174$ & $173$ & $177$\\
\hline
\end{tabular}
\end{center}

\begin{center}
\footnotesize
\begin{tabular}{lcccccccc}
Residue & pop-97 & pop-80 \\
\hline Alanine   & $4$ & $47$ \\
Arginine         & $2$ & $23$ \\
Asparagine       & $2$ & $15$ \\
Aspartate        & $3$ & $20$ \\
Cysteine         & $0$ & $\phantom{0}5$ \\
Glutamate        & $3$ & $34$ \\
Glutamine        & $2$ & $18$ \\
Glycine          & $2$ & $15$ \\
Histidine        & $1$ & $\phantom{0}9$ \\
Isoleucine       & $6$ & $40$ \\
Leucine          & $7$ & $59$ \\
Lysine           & $3$ & $27$ \\
Methionine       & $0$ & $\phantom{0}8$ \\
Phenylalanine    & $2$ & $20$ \\
Proline          & $7$ & $80$ \\
Serine           & $2$ & $27$ \\
Threonine        & $3$ & $33$ \\
Tryptophan       & $0$ & $\phantom{0}8$ \\
Tyrosine         & $2$ & $18$ \\
Valine           & $7$ & $50$ \\
\hline
\end{tabular}
\end{center}

\begin{center}
\footnotesize
\begin{tabular}{lccccc}
&  \multicolumn{2}{c}{Empirical} & ~~~& \multicolumn{2}{c}{Theoretical}\\\cline{2-3}\cline{5-6}
Residue & $\phi$ & $\psi$ & & $\phi$ & $\psi$ \\
\hline Alanine   & $-66.7^{\circ}$ & $-13.1^{\circ}$ & & $-60^{\circ}$ & $-15^{\circ}$\\
                 & $-52.1^{\circ}$ & $-33.6^{\circ}$ & &\\
                 & $-51.9^{\circ}$ & $-37.9^{\circ}$ & &\\
Arginine         & $-79.2^{\circ}$ & $-20.2^{\circ}$ & & $-70^{\circ}$ & ~\,$-5^{\circ}$ \\
		 &	&	& & $-70^{\circ}$ & $-25^{\circ}$\\
		 &	&	& & $-60^{\circ}$ & $-15^{\circ}$ to $-10^{\circ}$\\
		 &	&	& & $-55^{\circ}$ & $-30^{\circ}$\\
                 &      &       & & $-40^{\circ}$ & $-50^{\circ}$\\      
Asparagine       & $-94.8^{\circ}$ & ~\,$-3.4^{\circ}$ & & $-50^{\circ}$ & $-40^{\circ}$ \\
                 &      &       & & $-50^{\circ}$ & $-30^{\circ}$\\
		 &      &       & & $\phantom{-}70^{\circ}$ & ~\,$-5^{\circ}$\\
Aspartate        & $-79.4^{\circ}$ & $\phantom{-}83.0^{\circ}$ & & $\phantom{-}70^{\circ}$ & ~\,$-5^{\circ}$ \\
Cysteine         & $-87.7^{\circ}$ & $-45.1^{\circ}$ & & $\phantom{-}60^{\circ}$ & $-40^{\circ}$ \\
Glutamate        & $-55.0^{\circ}$ & $-49.9^{\circ}$ & & $-60^{\circ}$ & $-15^{\circ}$\\
Glutamine        & $-65.5^{\circ}$ & $-24.0^{\circ}$ & & $\phantom{-}70^{\circ}$ & ~\,$-5^{\circ}$\\
Glycine          & $\phantom{-}80.2^{\circ}$ & ~\,$\phantom{-}7.2^{\circ}$ & & $-75^{\circ}$ & $\phantom{-}20^{\circ}$  \\
                 &      &       & & $-75^{\circ}$ & $\phantom{-}50^{\circ}$\\
                 &      &       & & $-70^{\circ}$ & ~\,$\phantom{-}0^{\circ}$\\
                 &      &       & & $-65^{\circ}$ & $-10^{\circ}$\\
                 &      &       & & $-60^{\circ}$ & $-15^{\circ}$\\
                 &      &       & & $-50^{\circ}$ & $-25^{\circ}$\\
                 &      &       & & $\phantom{-}70^{\circ}$ & $-15^{\circ}$\\
                 &      &       & & $\phantom{-}75^{\circ}$ & $-30^{\circ}$\\
Histidine        & $\phantom{-}51.2^{\circ}$ & $\phantom{-}32.4^{\circ}$ & & $-180^{\circ}$ & ~$155^{\circ}$  \\
		 &	 &	& & $-80^{\circ}$ & $170^{\circ}$ to $175^{\circ}$ \\
                 &       &      & & $-80^{\circ}$ to $-75^{\circ}$ & ~$130^{\circ}$ \\
Isoleucine      & $-64.1^{\circ}$ & $-21.9^{\circ}$ & & $-55^{\circ}$ & $-25^{\circ}$ \\
		&	&	& & $-50^{\circ}$ & $-40^{\circ}$ \\
Leucine         & $-81.6^{\circ}$ & $-13.5^{\circ}$ & & $-70^{\circ}$ &  ~\,$-5^{\circ}$  \\
                & $-63.5^{\circ}$ & $-44.5^{\circ}$ & & & \\
                & $-60.9^{\circ}$ & $-29.3^{\circ}$ & & & \\
                & $-55.8^{\circ}$ & $-36.4^{\circ}$ & & & \\     
Lysine          & $\phantom{-}63.1^{\circ}$ & $\phantom{-}23.1^{\circ}$ & & $-45^{\circ}$ & $-45^{\circ}$ to $-40^{\circ}$ \\
Methionine      & $-67.5^{\circ}$ & $-27.5^{\circ}$ & & $\phantom{-}50^{\circ}$ & $-40^{\circ}$  \\
Phenylalanine   & $-50.3^{\circ}$ & \,\,$135.2^{\circ}$ & & $-45^{\circ}$ & $-40^{\circ}$  \\
                &       &       & & $\phantom{-}70^{\circ}$ & $-10^{\circ}$ \\
Proline         &  $-63.8^{\circ}$ & $-21.6^{\circ}$ & & $-55^{\circ}$ & $-20^{\circ}$  \\
Serine          & $-58.1^{\circ}$ & $-27.3^{\circ}$ & & $\phantom{-}65^{\circ}$ & $-45^{\circ}$ \\
		& $-103.4^{\circ}$ & $\phantom{-}\phantom{0}1.1^{\circ}$ & & & \\
Threonine       & $-57.4^{\circ}$ & $-17.3^{\circ}$ & & $-45^{\circ}$ & $-45^{\circ}$  \\
Tryptophan      & $-68.0^{\circ}$ & $-62.3^{\circ}$ & & $\phantom{-}65^{\circ}$ & $-40^{\circ}$ to $-35^{\circ}$  \\
		&       &       & & $\phantom{-}70^{\circ}$ & $-55^{\circ}$  \\
Tyrosine        & $-67.6^{\circ}$ & ~\,$-9.8^{\circ}$ & & $-50^{\circ}$ & $-40^{\circ}$ to $-35^{\circ}$ \\
                &       &       & & $-45^{\circ}$ & $-45^{\circ}$ \\
Valine          & $-56.2^{\circ}$ & $-31.7^{\circ}$ & & $-55^{\circ}$ & $-25^{\circ}$  \\
\hline
\end{tabular}
\end{center}
